Hydra Battles and Cie

### 2021-08-30 doc/part-hydras.tex
using inputsnippets (chapter 3, up to page 59 of the pdf)

\input{movies/snippets/ON_plus/compareDef}

\input{movies/snippets/ON_plus/compareCorrect}

\input{movies/snippets/ON_plus/plusComp}

The Lemma \texttt{Wellfounded.Disjoint\_Union.wf\_disjoint\_sum} of Standard Library
helps us to prove that our order \texttt{lt} is well-founded.

\input{movies/snippets/ON_plus/ltWf}

Then, we can build an instance of \texttt{ON}:

\input{movies/snippets/ON_plus/OnPlus}

@@

\input{movies/snippets/ON_mult/Defs}

@@

\input{movies/snippets/ON_Omega2/Omega2Def}

\input{movies/snippets/ON_Omega2/Defs}

@@

\input{movies/snippets/ON_Omega2/Defs}

@@

\input{movies/snippets/ON_Omega2/plusDef}

@@

\input{movies/snippets/ON_Omega2/multFinDef}

@@

\input{movies/snippets/ON_Omega2/uniqueDecomposition}

>>>>

\inputsnippets{ON_plus/compareDef,
  ON_plus/compareCorrect, ON_plus/plusComp}

The Lemma \texttt{Wellfounded.Disjoint\_Union.wf\_disjoint\_sum} of Standard Library
helps us to prove that our order \texttt{lt} is well-founded, thenwe can build an instance of \texttt{ON}:

\inputsnippets{ON_plus/ltWf, ON_plus/OnPlus}

@@

\inputsnippets{ON_mult/Defs}
\inputsnippets{ON_mult/multComp,  ON_mult/ONMult}
\inputsnippets{ON_mult/endDefs}

@@

\inputsnippets{ON_Omega2/Omega2Def, ON_Omega2/Defs}

@@

\input{movies/snippets/ON_Omega2/succ}

@@

\inputsnippets{ON_Omega2/plusDef, ON_Omega2/plusExamples}

@@

\input{movies/snippets/ON_Omega2/multFinDef}
\input{movies/snippets/ON_Omega2/multFinExamples}

@@

\inputsnippets{ON_Omega2/uniqueDecompositiona,
  ON_Omega2/uniqueDecompositionb,
  ON_Omega2/uniqueDecompositionz}
